\section{\sc Academic Service}
% Cons:
% 	•	Descriptions sometimes blend in with unrelated experiences (e.g., outreach vs organizing).
% 	•	Formatting of events (e.g., event links) inconsistent.

\vspace{35pt}
\section{\sl Reviewer for Scientific Journals}
{\bf Theoretical Chemistry Accounts}  \hfill \textit{Mar. 2025}\\ 
Reviewed a theoretical chemistry manuscript involving reaction mechanisms and astrochemical relevance.

\section{\sl Organisation of \\ Conferences, Seminars \&  Workshops}

{\bf Co-organiser - Finite Systems Department Seminar}  \hfill \textit{Feb. 2025}\\ 
Max Planck Institute for the Physics of Complex Systems \hfill Germany \\
Organised a departmental seminar, managed speaker invitations, coordinated schedules, and facilitated collaboration and knowledge exchange.

   
{\bf Co-organiser - 1$^{st}$ Taiwan$-$Philippines Workshop} \hfill \textit{Oct. 2017} \\
Institute of Chemistry, Academia Sinica \hfill Taiwan \\
Managed overall event organisation, including scheduling, speaker coordination, and participant engagement.

{\bf Coordinator - Growing Career Workshop} \hfill \textit{Feb. 2017} \\
Institute of Chemistry, Academia Sinica \hfill Taiwan \\
Handled programme logistics and planning, supporting career development and enhancing professional skills for graduate students.

\section{\sl Volunteer \&  Leadership Roles}

{\bf Volunteer - 10$^{th}$ Woman in Physical and Chemical Science Workshop}
\hfill \textit{Oct. 2017} \\
The Society of Taiwan Women in Science and Technology \hfill Taiwan \\
Coordinated speaker sessions, facilitated networking, and promoted visibility for women in science.   \hfill \href{http://www.twepress.net/new/activity/item/213-activity-117-4}{[Event Link]}

{\bf Volunteer - 8$^{th}$  Asian Consortium on Computational Material Science}  \hfill \textit{June 2015} \\ 
Institute of Atomic and Molecular Sciences, Academia Sinica \hfill Taiwan \\
Assisted in organising and coordinating the event, designed promotional materials, and supported logistical activities. \hfill \href{https://www.iams.sinica.edu.tw/accms8/}{[Event Link]}

\section{\sl Outreach \& \\ Public Speaking}

{\bf Distinguished Speaker - Lecture on Scientific Conference Planning} \hfill \textit{May 2024}  \\
Junior Chemist Society, Institute of Chemistry, Academia Sinica \hfill Taiwan  \\
Delivered presentations on effective scientific conference planning, sharing academic and cultural experiences from the US, UK, and Germany. \hfill \href{https://www.facebook.com/share/p/15W3mzVk48/?mibextid=wwXIfr}{[Event Link]}

{\bf Speaker - Taiwan Academic Talents Overseas Advancement Program}
\hfill \textit{Dec. 2019} \\
National Sciences and Technology Council \hfill Taiwan  \\
Spoke on pursuing academic careers abroad, offering insights on research opportunities, cultural adaptation, and international collaboration.

{\bf Speaker - Chemical Society National Meeting}
\hfill \textit{Dec. 2016} \\
\null \hfill Taiwan  \\
%   Target audience: Professors
Delivered a talk focused on motivating graduate students through effective mentorship, goal-setting, and supportive research environments.

{\bf  Public Lecturer - International Academic Competence Conference} \hfill \textit{Dec. 2013} \\
National Taiwan University \hfill Taiwan  \\
%   Target audience: The general public
Provided a public lecture simplifying complex quantum mechanics concepts using visual aids and relatable analogies. \hfill \href{https://iac2013.weebly.com}{[Event Link]}

\endinput