\section{\sc Research Presentations}

% Pros:
% 	•	Very diverse, includes invited talks and oral/poster presentations.
% 	•	Demonstrates international visibility.

% Cons:
% 	•	Links are repeated or broken across lines in PDF.
% 	•	Overly long list; can be overwhelming.

% Suggestions:
% 	•	Split into sections:
% 	•	Invited Talks
% 	•	Oral Presentations
% 	•	Posters
% 	•	Highlight 3–5 selected, most impactful talks.
% 	•	Add presentation titles in quotes consistently.


% \emph{title in italic}
\vspace{25pt}

\section{\sl Invited Talks}

{\bf The Mixed-Gen Lecture Series} \hfill \textit{May 2025} \\
Taiwan Theoretical and Computational Molecular Sciences Association \hfill Taiwan\\
National Center for Theoretical Sciences - Physics Division \hfill (Online) \\
"\href{https://www.t2comsa.tw/newmixed-gen-lecture-series-20250508/}{Calculating excitonic interactions using transition currents with application to PTCDA}" 


{\bf The Finite Systems Department Seminar}  \hfill \textit{Feb. 2023}\\ 
Max Planck Institute for the Physics of Complex Systems \hfill Germany \\
"From Physical Chemistry to More Physical Projects"
   
{\bf Atmospheric, Planetary and Theoretical Chemistry Seminar} \hfill \textit{Jan. 2023} \\
School of Chemistry, University of Leeds \hfill UK \\
"Electron-Molecule Collision of Hydrofluoroolefins"

{\bf 11$^{\text{th}}$ International Meeting on Photodynamics and Related Aspects} \hfill \textit{Nov. 2022}\\
"\href{https://photodynamics.instec.cu/pages/speakersconfirm.php}{Using Coherent States to Study Dynamics of Rydberg Atom Chain}" \hfill Cuba

{\bf 1$^{st}$ Symposium and Workshop on First-Principles Calculations} \hfill \textit{Aug. 2022} \\
University of the Philippines Los Banos \hfill Philippines \\
\emph{"Using the Moving Grids in Both Chemistry and Physics"}  \hfill (Online) 

\section{\sl Selected Oral Presentations}

{\bf 88${^\text{th}}$ Deutsche Physikalische Gesellschaft}
\hfill \textit{Mar. 2025} \\
"\href{https://www.dpg-verhandlungen.de/year/2025/conference/bonn/part/mo/session/30/contribution/7}{Calculating excitonic interactions using transition currents with }
\hfill Germany \\
\href{https://www.dpg-verhandlungen.de/year/2025/conference/bonn/part/mo/session/30/contribution/7}{application to PTCDA}"

{\bf 87${^\text{th}}$ Deutsche Physikalische Gesellschaft} \hfill \textit{Mar. 2024} \\
"\href{https://www.dpg-verhandlungen.de/year/2024/conference/berlin/part/o/session/15/contribution/3}{Interaction Between Polyatomic Molecules on Layered Surfaces}
\hfill Germany \\
\href{https://www.dpg-verhandlungen.de/year/2024/conference/berlin/part/o/session/15/contribution/3}{beyond the Dipole Approximation}"

{\bf Kinetic Monte Carlo Modeling Workshop}
\hfill \textit{July 2017}\\
"How do we Design an Artificial Catalyst for Hydrogen \hfill Taiwan \\
Gas Production: Lessons from the Key Reaction Mechanism"

{\bf Theoretical and Computational Molecular Sciences Association}
\hfill \textit{Sept. 2014}\\
"Spectroscopic Study of the O--H Stretching Motions in \hfill Taiwan \\
$\mathrm{H^+(CH_3OH)_{1-3}X_{0-2}}$,
X=Ar and N$_2$"

{\bf  69$^{\text{th}}$ International Symposium on Molecular Spectroscopy}
\hfill \textit{June 2014}\\
"The Free O--H Anharmonic Stretching Motions in $\mathrm{H^+(CH_3OH)_{1-3}}$ \hfill USA \\
with/ without Attached Argon"

\section{\sl Selected Poster Presentations}
{\bf Coherent Control with Modified Vacuum Fields}
\hfill \textit{Aug. 2024} \\
"Interaction between polyatomic molecules on layered surfaces \hfill Sweden \\
- beyond the dipole approximation"

{\bf Path Integral Quantum Mechanics Workshop}
\hfill \textit{June 2023} \\
"Preserve Non-Stationary Long-Term Dynamics via Selected \hfill Israel \\
Incomplete Dual
Bases"  


{\bf Spectroscopy and Dynamics Group Annual Conference}
\hfill \textit{Apr. 2022} \\
"Building a Many-Body Wave Function with Less Computational 
\hfill UK\\
Cost: Coupled-Coherent State"

{\bf  NTU Graduate Student Poster Presentation}
\hfill \textit{June 2020} \\
"A General Method for Probing a Special Reaction with the
\hfill Taiwan \\
Intrinsic Selectivity is Developed by Modifying one of the Reaction Coordinates"

% \item TIGP Graduate Student Poster Presentation
% \hfill \textit{May 2017}\\
% "Calculate vibronic coupling for proton-coupled electron transfer mechanism with SF-TDDFT (MPWB1K)"        
% \hfill Taiwan 

{\bf Chemical Society National Meeting}
\hfill \textit{Feb. 2016}\\
"Interstellar Glycine Formation: Can O--H Dangling Bond on the 
\hfill Taiwan \\
Icy Grain Reduce the Barrier?"

% \item TIGP Graduate Student Poster Presentation
% \hfill \textit{May 2016}\\
% "Before the Design of Molecular Catalyst for H$_2$ Production: Concerted Proton-Coupled Electron Transfer Mechanism"
% \hfill Taiwan 

{\bf 8$^{th}$ Asian Consortium on Computational Materials Science}
\hfill \textit{June 2015}\\
"Anharmonicity Calculation of O--H Stretching Motion in Small Methanol
\hfill Taiwan \\
 Clusters along Normal Coordinates" 

{\bf Spring Symposium of Photochemistry}
\hfill \textit{Jan. 2014}\\
"Theoretical Investigation of H$^+$(MeOH)$_n$ Vibrational Spectroscopy 
\hfill Taiwan \\
with/without Argon Attachment, n=1-4"

{\bf Asian Core Winter School}
\hfill \textit{Jan. 2013}\\
"Theoretical study on proton transfer dynamics of $\mathrm{((CH_3)_3N)_2}$--H$^+$--R"
\hfill South Korea 

\endinput